Intersection Fusion Moves \\ Fusion Moves for Multicut Objectives

### 2014-10-08 paper/egpaper_for_review.tex
improvment

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
\usepackage{amsthm}
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{setspace}
%for tikz
\usepackage{tikz,pgfplots}
\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
\usetikzlibrary{arrows,petri,topaths}
\usetikzlibrary{positioning,fit,calc}
\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}

@@

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}
%%%%%%%%% TITLE
\include{my_macros.tex}
\title{FancyMc Moves \\ Fusion Moves for Multicut Objectives}

@@

The tale of the multicut

@@

\begin{theorem}[NameMe]
Solving ??? and ??? will never increase the best energy...
\end{theorem}

@@

\begin{theorem}[NameMe]
If the all cut edges of the global optimal
solution are included in the union of
the cut edges of two proposals, solving
??? will find the global optimal solution
\end{theorem}

>>>>

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
\usepackage{amsthm}
\usepackage{dirtytalk}
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{setspace}
%for tikz
\usepackage{tikz,pgfplots}
\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
\usetikzlibrary{arrows,petri,topaths}
\usetikzlibrary{positioning,fit,calc}
\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}

@@

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}
%%%%%%%%% TITLE
\include{my_macros.tex}
\title{Intersection Fusion Moves \\ Fusion Moves for Multicut Objectives}

@@

  Nunez-Iglesias \etal describe the multicut as
  \say{one-shot agglomeration of supervoxels} whose 
  main drawback is the scalability \cite{nunez_iglesias_2013}.
  Within this work we will overcome the scalability issues.

@@

\begin{theorem}[NameMe]
Let $x_{a}$ and $x_{b}$ be two proposal solutions and  $x_{new}$ the solution of \ref{???}.
$x_{new}$  will never decrease the energy:
$x_{new} \cdot w \leq  \min( x_{a}\cdot w,  x_{b}\cdot w) $ 
\end{theorem}

@@

\begin{theorem}[NameMe]

Let $x_{a}$ and $x_{b}$ be two proposal solutions and  $x_{opt}$ the global solution,
$X_{a}^c, X_{b}^c$ and $ X_{opt}^c$ the set of cut edges in  $x_{a}, x_{b}$  and $ x_{opt}$
optimal solution.
Iff  $ X_{opt}^c \subseteq  (X_{a}^c \cup X_{b}^c)$,  the solution of \ref{???} will be $x_{opt}$.
\end{theorem}
